InteroceptionScale - Data Analysis

### 2024-11-21 study1/analysis/2_analysis.qmd
added items
not a fun task

# labels <- list(
#   Anxious_State_Q4 = "Blablagl re'f sdf",
#   sref
# )
# 
# Make 
```

>>>>

labels <- list(
  Anxious_State_Q4 = "Blablagl re'f sdf",
  Sexual_State_Q1: "I always know when I am sexually aroused",
  Sexual_State_Q2: "I always feel in my body if I am sexually aroused",
  Sexual_State_Q3:
        "My body is always in the same specific state  when I am sexually aroused",
  Sexual_State_Q4:
        "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)",
  Sexual_State_Q5:
        "I can always tell that I am sexually aroused from the way I feel inside",
  Sexual_State_A: "I always know that I am attentively doing a study", // 'A' stands for attention
  Sexual_Cardiac_Q1:
        "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
  Sexual_Respiratory_Q1:
        "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
  Sexual_Gastric_Q1:
        "When I am sexually aroused, I often feel changes in my stomach (e.g., bloating, rumbling, discomfort)",
  Sexual_Gastric_Q2:
        "When I am sexually aroused, I often feel butterflies in my stomach",
  Sexual_Genital_Q1:
        "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
  Sexual_Genital_Q2:
        "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
  Sexual_SkinThermo_Q1:
        "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)",
  Sexual_SkinThermo_Q2:
        "When I am sexually aroused, I often feel like some areas of my skin become sweaty (e.g., palms, back, forehead)",
  Sexual_SkinThermo_Q3:
        "When I am sexually aroused, I often feel my mouth becoming dry",
  Sexual_ColonBladder_Q1:
        "When I am sexually aroused, I often feel like I need to relieve myself by urinating or defecating",
  Sexual_ColonBladder_Q2:
        "During sex or masturbation, I often feel like I need to relieve myself by urinating or defecating",
  Anxious_State_Q1: "I always know when I am anxious",
  Anxious_State_Q2: "I always feel in my body if I am anxious",
  Anxious_State_Q3:
        "My body is always in the same specific state when I am anxious",
  Anxious_State_Q4:
        "Being anxious is a very different bodily feeling compared to other states (e.g., feeling sexually aroused, relaxed or after exercise)",
  Anxious_State_Q5:
        "I often realize that I am anxious only when others tell me",
  Anxious_Cardiac_Q1:
        "When I am anxious, I often feel changes in the way my heart beats (e.g., faster or stronger)",
  Anxious_Respiratory_Q1:
        "When I am anxious, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
  Anxious_Gastric_Q1:
        "When I am anxious, I often feel changes in my stomach (e.g., bloating, rumbling, discomfort)",
  Anxious_Genital_Q1:
        "When I am anxious, I often notice specific sensations in my genital area (e.g., contractions, dryness)",
  Anxious_SkinThermo_Q1:
        "When I am anxious, I often feel changes in my temperature (e.g., feeling warm or cold)",
  Anxious_SkinThermo_Q2:
        "When I am anxious, I often feel like some areas of my skin become sweaty (e.g., palms, back, forehead)",
  Anxious_SkinThermo_Q3:
        "When I am anxious, I often feel my mouth becoming dry",
  Anxious_SkinThermo_Q4:
        "When I am anxious, I often have difficulty swallowing",
  Anxious_SkinThermo_A:
        "Even if I am anxious, I should now answer all the way to the left",
  Anxious_ColonBladder_Q1:
        "When I am anxious, I often feel like I need to relieve myself by urinating or defecating",
  Nociception_State_Q1: "I always feel in my body if I am ill",
  Nociception_State_Q2:
        "I can easily tell when I am feeling ill (e.g., nauseous or sick)",
  Nociception_Cardiac_Q1:
        "I often feel painful sensations coming from my heart",
  Nociception_Cardiac_Q2:
        "I often experience painful sensations coming from my chest",
  Nociception_Respiratory_Q1:
        "I often feel like I have difficulties breathing normally",
  Nociception_Respiratory_Q2:
        "I often feel like I can't get enough oxygen by breathing normally",
  Nociception_Gastric_Q1: "I often feel pain in my stomach",
  Nociception_Genital_Q1:
        "My genital organs are very sensitive to pleasant stimulations",
  Nociception_Genital_Q2:
        "My genital organs are very sensitive to painful stimulations",
  Nociception_SkinThermo_Q1:
        "My skin is very sensitive to painful stimulations (e.g., pinching)",
  Nociception_SkinThermo_Q2:
        "My skin is very sensitive to pleasant stimulations (e.g., caressing)",
  Nociception_SkinThermo_Q3:
        "Changes in temperature (e.g., feeling feverish or cold) are the first things I notice when I am becoming ill",
  Nociception_ColonBladder_Q1:
        "I often experience a pleasant sensation when relieving myself when urinating or defecating)",
  Nociception_ColonBladder_Q2:
        "I often experience painful sensations when relieving myself when urinating or defecating",
  Nociception_ColonBladder_A:
        "I often experience sensations, and I will answer zero to this question",
  Sensitivity_State_Q1: "I always know when I am relaxed",
  Sensitivity_State_Q2: "I always feel in my body if I am relaxed",
  Sensitivity_State_Q3:
        "My body is always in the same specific state when I am relaxed",
  Sensitivity_State_Q4:
        "Being relaxed is a very different bodily feeling compared to other states (e.g., feeling anxious, sexually aroused or after exercise)",
  Sensitivity_State_Q5:
        "When something important is happening in my life, I can feel it in my body",
  Sensitivity_Cardiac_Q1:
        "In general, I am very sensitive to changes in my heart rate",
  Sensitivity_Cardiac_Q2: "I often notice changes in my heart rate",
  Sensitivity_Cardiac_Q3:
        "I can notice even very subtle changes in the way my heart beats",
  Sensitivity_Cardiac_Q4:
        "I am always very aware of my heartbeats, even when I am calm",
  Sensitivity_Cardiac_Q5:
        "I only notice my heart when it is thumping in my chest",
  Sensitivity_Cardiac_Q6:
        "I often try to feel my heart with my hands (e.g., by putting my hand on my chest)",
  Sensitivity_Cardiac_Q7:
        "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
  Sensitivity_Cardiac_A:
        "In general, I am very sensitive and attentive to the questions I am currently answering",
  Sensitivity_Respiratory_Q1:
        "In general, I am very sensitive to changes in my breathing",
  Sensitivity_Respiratory_Q2: "I often notice changes in my breathing",
  Sensitivity_Respiratory_Q3:
        "I can notice even very subtle changes in my breathing",
  Sensitivity_Respiratory_Q4:
        "I am always very aware of how I am breathing, even when I am calm",
  Sensitivity_Respiratory_Q5:
        "I often only notice how I am breathing when it becomes loud",
  Sensitivity_Respiratory_Q6:
        "I often only notice how I am breathing when my breathing becomes shallow or irregular",
  Sensitivity_Respiratory_Q7:
        "When something important is happening in my life, I can immediately feel changes in my breathing",
  Sensitivity_Gastric_Q1:
        "In general, I am very sensitive to what my stomach is doing",
  Sensitivity_Gastric_Q2:
        "I can notice even very subtle changes in what my stomach is doing",
  Sensitivity_Gastric_Q3:
        "I am always very aware of what my stomach is doing, even when I am calm",
  Sensitivity_Gastric_Q4: "I often check the smell of my own breath",
  Sensitivity_Gastric_Q5: "I often check the smell of my farts",
    ensitivity_Gastric_Q6: "I often pay attention to the noises of my stomach",
    Sensitivity_Gastric_A: "I often pay attention to the answers I am giving",
    Sensitivity_Genital_Q1:
        "In general, I am very sensitive to changes in my genital organs",
    Sensitivity_Genital_Q2:
        "I can notice even very subtle changes in the state of my genital organs",
    Sensitivity_Genital_Q3:
        "I am always very aware of the state of my genital organs, even when I am calm",
    Sensitivity_SkinThermo_Q1: "In general, my skin is very sensitive",
    Sensitivity_SkinThermo_Q2:
        "I can notice even very subtle stimulations to my skin (e.g., very light touches)",
    Sensitivity_SkinThermo_Q3:
        "I can notice even very subtle changes if my skin becomes dry or sweaty",
    Sensitivity_SkinThermo_Q4:
        "I am always very aware if my hands and feet are cold or warm",
    Sensitivity_SkinThermo_Q5: "I often check the smell of my armpits",
    Sensitivity_SkinThermo_Q6: "I am very prone to having goosebumps",
    Sensitivity_SkinThermo_Q7:
        "My skin is susceptible to itchy fabrics and materials",
    Sensitivity_SkinThermo_Q8:
        "I enjoy the sensations of touching different materials (e.g., soft fabrics, wooden objects, smooth surfaces)",
    Sensitivity_ColonBladder_Q1:
        "In general, I am very aware of the sensations that are happening when I am defecating",
    Sensitivity_ColonBladder_Q2:
        "In general, I am very aware of the sensations that are happening when I am urinating",
    Sensitivity_ColonBladder_Q3: "I often check the colour of my urine",
    Sensitivity_ColonBladder_Q4: "I often check the colour of my faeces",
    Accuracy_State_Q1: "I can always accurately feel when I am about to cough",
    Accuracy_State_Q2: "I can always accurately feel when I am about to sneeze",
    Accuracy_State_Q3: "I can always accurately feel when I am about to vomit",
    Accuracy_State_Q4:
        "I can always accurately feel when I am starting to be hungry",
    Accuracy_State_Q5:
        "I can always accurately feel when I am starting to be thirsty",
    Accuracy_Cardiac_Q1:
        "I can always accurately feel if my heart rate is slow or fast",
    Accuracy_Cardiac_Q2:
        "I sometimes feel like my heart is racing or beating faster than usual, but when I check my pulse, it is not as intense as I thought",
    Accuracy_Respiratory_Q1:
        "I can always accurately feel how I am breathing (e.g., fast or slow, deep or shallow)",
    Accuracy_Respiratory_A:
        "I can always accurately answer to the left on this question to show that I am reading it",
    Accuracy_Gastric_Q1: "I can always accurately feel when I am about to fart",
    Accuracy_Gastric_Q2: "I can always accurately feel when I am about to burp",
    Accuracy_Gastric_Q3: "I often feel thirsty even if I drank recently",
    Accuracy_Gastric_Q4:
        "I don't always feel the need to drink until I am really thirsty",
    Accuracy_Gastric_Q5: "I often feel hungry even if I ate recently",
    Accuracy_Gastric_Q6:
        "I don't always feel the need to eat until I am really hungry",
    Accuracy_Gastric_Q7:
        "I often sneeze suddenly without feeling the need building up",
    Accuracy_Gastric_Q8:
        "I sometimes feel that burping will produce some relief but then it doesn't",
    Accuracy_Genital_Q1:
        "I can always accurately perceive if my genital organs are in a state of arousal (e.g., hard, wet, pulsating)",
    Accuracy_Genital_Q2:
        "I sometimes feel like I am sexually aroused, but when I try to satisfy the feeling, I realise that I am not as sexually aroused as I initially thought",
    Accuracy_Genital_A:
        "I can always accurately perceive that to this question I should answer the lowest option",
    Accuracy_SkinThermo_Q1:
        "I can always accurately feel when something is going to be itchy",
    Accuracy_SkinThermo_Q2:
        "I can always accurately feel when I start to have a fever",
    Accuracy_SkinThermo_Q3:
        "When something touches my skin, I can always accurately feel if it's hot or cold",
    Accuracy_SkinThermo_Q4:
        "I sometimes feel my skin itching, but when I scratch it, it doesn't produce the relief I expected",
    Accuracy_ColonBladder_Q1:
        "I often feel the need to urinate even when my bladder is not full",
    Accuracy_ColonBladder_Q2:
        "I don't always feel the need to urinate until my bladder is very full",
    Accuracy_ColonBladder_Q3:
        "I often feel the need to defecate even when my intestine is not full",
    Accuracy_ColonBladder_Q4:
        "I don't always feel the need to defecate until my intestine is very full",
    Accuracy_ColonBladder_Q5:
        "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
    Confusion_State_Q1:
        "Sometimes I can't tell if the sensations in my body are good or bad",
    Confusion_State_Q2:
        "Sometimes I am confused about what sensations in my body mean",
    Confusion_Cardiac_Q1:
        "Sometimes my heart starts racing and I often don't know why",
    Confusion_Respiratory_Q1:
        "Sometimes my breathing becomes erratic or shallow and I often don't know why",
    Confusion_Gastric_Q1:
        "Sometimes I feel negative and realise after eating that I was just hungry",
    Confusion_Gastric_Q2:
        "Sometimes I don't realise I was hungry until I ate something",
    Confusion_Genital_Q1:
        "Sometimes I notice arousal in my genital areas (e.g., stiffness, wetness) when I am not feeling sexually aroused",
    Confusion_SkinThermo_Q1:
        "Sometimes I have sensations on my skin (e.g., itches, goosebumps) without any clear cause",
    Confusion_ColonBladder_Q1:
        "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
    Confusion_ColonBladder_A:
        "Sometimes I notice that I need to answer all the way to the right",
#   sref
# )

# Make 
```
